---
title: "How to extract coordinates and sequence from a fasta file"
output: html_document
date: "2024-06-04"
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

## Installing Rust

First you need to have an updated Rust installation. Go to this [site](https://www.rust-lang.org/tools/install) to learn how to install Rust.


## Installing rustytools

You will need to have the devtools package installed...

```{r, eval=F}
devtools::install_github("furlan-lab/rustytools")
```


## Running a tool to extract consensus sequence data

Loading libraries
```{r, dpi=300, fig.height=4, fig.width = 6}
rm(list=ls())
suppressPackageStartupMessages({
  library(rustytools)
})

```

## Get consensus from fasta

This function will process a fasta file that has been processed using a tool such as samtools consensus.  The function will find all regions (subsequences) of the fasta that have sequence (A, C, T, G) and output a granges object containing the features and their sequences.  It is invoked as follows:

```{r}
fasta="~/Desktop/GENDX_HLA_Mix1_S1_L001_t1000.fa"
tfasta="~/Desktop/test.fa"
results<-get_consensus(tfasta, cores=1, split=1)
results<-get_consensus(fasta, cores=1, split=10000)
debug(get_consensus)
```

## Appendix
```{r Appendix}
sessionInfo()
```
